|

### 2023-07-17 paper/01-introduction.Rmd
address page 3 comment (#12)

Our focus of this manuscript is specifically on measuring the performance of defensive linemen in the NFL. There are two main types of defensive linemen in American football: (1) defensive tackles (DTs) located within the interior of the line and (2) defensive ends (DEs) located along the edges; see Figure \ref{fig:formation} (top) for example formation with DTs and DEs. The primary purpose of both positions is to rush the QB on passing plays, with DEs displaying superiority in observed pass rushing ability [@Eager2018nfl]. Additionally, within DTs there are nose tackles (NTs) who directly line up across from the ball at the line of scrimmage; see Figure \ref{fig:formation} (bottom) for example defensive formation with a NT. Typically, teams will employ either one NT or two DTs on the interior with DEs along either side of the defensive line. In addition to defensive lineman, other positions may attempt to rush the QB on blitzing plays such as outside linebackers (OLBs), interior linebackers (ILBs), and potentially members of the secondary (cornerback, free safety, strong safety) who typically play pass coverage.

>>>>

Our focus of this manuscript is specifically on measuring the performance of defensive linemen in the NFL.
There are two main types of defensive linemen in American football: (1) defensive tackles (DTs) and (2) defensive ends (DEs).
Typically, DTs and DEs are located within the interior of the line and along the edges, respectively; see Figure \ref{fig:formation} (top) for example formation with DTs and DEs.
The primary purpose of both positions is to rush the QB on passing plays, with DEs displaying superiority in observed pass rushing ability [@Eager2018nfl].
Additionally, within DTs there are nose tackles (NTs) who directly line up across from the ball at the line of scrimmage; see Figure \ref{fig:formation} (bottom) for example defensive scheme with a NT.
NFL teams often employ either one NT or two DTs on the interior with DEs along either side of the defensive line.
In addition to defensive lineman, other positions may attempt to rush the QB on blitzing plays such as outside linebackers (OLBs), interior linebackers (ILBs), and potentially members of the secondary (cornerback, free safety, strong safety) whose primary role is pass coverage.
Note that apart from the formations shown in Figure \ref{fig:formation}, defensive linemen can have the flexibility to line up differently.
For example, a defensive end, depending on their opposing matchup, may not necessarily be positioned toward the outside of the line of scrimmage.

### 2023-07-17 paper/04-results.Rmd
address page 3 comment (#12)

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the varying intercept distributions for the top ten pass rushers for each position.
We obtain similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (defensive end), T.J. Watt (outside linebacker), Aaron Donald (defensive tackle), and Vita Vea (nose tackle) as the first-ranked pass rusher for their respective position.
We observe different levels of variability across these top players, with only a subset of players with intercept ranges strictly above zero.
This is not necessarily surprising given the limited sample of data.

[TODO: edit the below? McKinley still there but we did control for team effects]

Additionally, we are ignoring correlated performance between defensive linemen on the same team.
For instance, the top two defensive ends, Myles Garrett and Takkarist McKinley (see the top panel of Figure \ref{fig:fig_rankings_boot}), were teammates on the Cleveland Browns during this period of time.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an elite pass rusher.
We leave the exploration of adjusting for teammates for future work.

>>>>

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the varying intercept distributions for the top ten pass rushers for each position.
We obtain similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (defensive end), T.J. Watt (outside linebacker), Aaron Donald (defensive tackle), and Vita Vea (nose tackle) as the first-ranked pass rusher for their respective position.
Additionally, we observe different levels of variability across these top players, with only a subset of players with intercept ranges strictly above zero.
This is not necessarily surprising given the limited sample of data.

<!-- [TODO: edit the below? McKinley still there but we did control for team effects] -->

<!-- Additionally, we are ignoring correlated performance between defensive linemen on the same team. -->
<!-- For instance, the top two defensive ends, Myles Garrett and Takkarist McKinley (see the top panel of Figure \ref{fig:fig_rankings_boot}), were teammates on the Cleveland Browns during this period of time. -->
<!-- McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an elite pass rusher. -->
<!-- We leave the exploration of adjusting for teammates for future work. -->

### 2023-07-17 paper/05-discussion.Rmd
address page 3 comment (#12)

Through multilevel modeling, we observe that the pass rusher explains more variation in their play-level STRAIN, followed by the possession team, the pass rushing team, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and pressure. However, our model is limited in that we only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects. The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true. For instance, if one player is known to be an elite pass rusher then the opposing blocking team may focus their blocking efforts on this player. This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values. In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach. The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models. We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].

>>>>

Through multilevel modeling, we observe that the pass rusher explains more variation in their play-level STRAIN, followed by the possession and pass rushing teams, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and pressure.
However, our model is limited in that we only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects.
The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true.
For instance, if one player is known to be an elite pass rusher then the opposing blocking team may focus their blocking efforts on this player. 
This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values.
As shown in Figure \ref{fig:fig_rankings_boot}, the first- and fourth-ranked defensive ends Myles Garrett and Takkarist McKinley were teammates on the Cleveland Browns during this period of time.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an great pass rusher.
In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach.
The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models.
We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].
